Structuring College Access

### 2025-02-13 index.qmd
pop out quotes

<style>
/* Remove the triangle marker from summary elements */
details summary {
  list-style: none; /* In some browsers, this alone may suffice */
}

/* For WebKit-based browsers (Chrome, Safari, etc.) */
details summary::-webkit-details-marker {
  display: none;
}
</style>

<div style="margin: 0.5em 0 0 0;">
<details style="margin: 0; padding: 0;">
  <summary>**Geomarkets**</summary>
<div style="font-size: 0.80em; margin-bottom: 0;">
> Boundaries [often] match formal political and educational divisions, reflecting natural channels of communication. Each major metro area is composed of several markets, usually corresponding to the inner city, a first ring of suburbs, and an outer ring of suburbs [@RN4982, p. 4].
</div>
</details>
</div>

@@

<div style="margin: 0.5em 0 0 0;">
<details style="margin: 0; padding: 0;">
  <summary>**@RN4982[chapter 3]**</summary>
<div style="font-size: 0.85em; margin-bottom: 0;">
> Our research has simply demonstrated what everyone has always known: communities with high levels of family income and parental education are also communities in which students have higher than average SATs and more far-reaching aspirations” [@RN4982, p. 42].
</div>
</details>
</div>

@@

<div style="margin: 0.5em 0 0 0;">
<details style="margin: 0; padding: 0;">
  <summary>**@RN4982[chapter 4]**</summary>
<div style="font-size: 0.85em; margin-bottom: 0;">
> The layering of collegiate competition is primarily a socioeconomic layering. The hierarchical structure of collegiate competition reflects the stratified social and economic dimensions of communities from which colleges draw their students. Competition among colleges, as admissions officers have told us for so long, is a matter of keeping company with one’s peers [@RN4982, p. 72].
</div>
</details>
</div>

@@

<div style="margin: 0.5em 0 0 0;">
<details style="margin: 0; padding: 0;">
  <summary> Recommendation: target Geomarkets, schools targeted by peer colleges</summary>
<div style="font-size: 0.85em; margin-bottom: 0;">
> On occasion, senior spokespersons for the profession worry that students outside the main market areas remain forgotten and hence, unchallenged. Inevitably, the increasing competition for students, the expense of travel and mailings, and internal political constraints compel institutions to concentrate their efforts where they will do the most good. The result is a natural reinforcing of the basic socioeconomic patterns that gave shape in the first place to the structure of college choice [@RN4982, p. 44].
</div>
</details>
</div>

>>>>

<p class="quote">Geomarkets</p>
<p style="display:none;">Boundaries [often] match formal political and educational divisions, reflecting natural channels of communication. Each major metro area is composed of several markets, usually corresponding to the inner city, a first ring of suburbs, and an outer ring of suburbs [@RN4982, p. 4].</p>

@@

<p class="quote">@RN4982[chapter 3]</p>
<p style="display:none;">Our research has simply demonstrated what everyone has always known: communities with high levels of family income and parental education are also communities in which students have higher than average SATs and more far-reaching aspirations” [@RN4982, p. 42].</p>

@@

<p class="quote">@RN4982[chapter 4]</p>
<p style="display:none;">The layering of collegiate competition is primarily a socioeconomic layering. The hierarchical structure of collegiate competition reflects the stratified social and economic dimensions of communities from which colleges draw their students. Competition among colleges, as admissions officers have told us for so long, is a matter of keeping company with one’s peers [@RN4982, p. 72].</p>

@@

<p class="quote">Recommendation: target Geomarkets, schools targeted by peer colleges</p>
<p style="display:none;">On occasion, senior spokespersons for the profession worry that students outside the main market areas remain forgotten and hence, unchallenged. Inevitably, the increasing competition for students, the expense of travel and mailings, and internal political constraints compel institutions to concentrate their efforts where they will do the most good. The result is a natural reinforcing of the basic socioeconomic patterns that gave shape in the first place to the structure of college choice [@RN4982, p. 44].</p>
